Nanocall: An Open Source Basecaller for Oxford Nanopore Sequencing Data

### 2016-03-17 paper-biorxiv/paper.tex
pore models

\paragraph{Pore Models.}
By sequencing known DNA [TODO: lambda??], ONT have been able to train \emph{pore models}, describing the currents that might be observed through the nanopore in various DNA contexts. As of the time of this writing, the models use DNA sequences of length 6 (``6-mers'') as context, and for each 6-mer, they contain the \emph{mean} $\mu_k$ and \emph{standard deviation} $\sigma_k$ of a Gaussian modelling the \emph{event mean}, and the \emph{mean} $\eta_k$ and \emph{standard deviation} $\gamma_k$ of an Inverse Gaussian modelling the \emph{event standard deviation}. These pore models are included in basecalled data produced by Metrichor, and they depend only on the chemistry being used, not on the specific sample. There are currently 3 models in use, 1 for the template strand and 2 for the complement strand.

>>>>

\paragraph{Pore Models.}

ONT provide \emph{pore models} describing the events that are expected to be observed for various DNA contexts. For the SQK-MAP006 data used in this paper, the models use DNA sequences of length 6 (``6-mers'') as context, and for each 6-mer, they contain the \emph{mean} $\mu_k$ and \emph{standard deviation} $\sigma_k$ of a Gaussian distribution modelling the \emph{event mean}, and the \emph{mean} $\eta_k$ and \emph{standard deviation} $\gamma_k$ of an Inverse Gaussian modelling the \emph{event standard deviation}. These pore models are included in the basecalled FAST5 files produced by Metrichor, and they depend only on the chemistry being used, not on the specific sample. There are currently three models in use, one for the template strand and two for the complement strand.
